Active deformation of the Shargyn Basin, a transpressional strike-slip intersection in western Mongolia.

### 2013-05-10 writing/paper/conclusion.tex
done with presentation

	We describe the basin as a combination of two active structures. A left-lateral compressional stepover on the Bogd Fault forms the Khantaishir range and the Shargyn Fault. A conjugate strike-slip intersection between the Bogd Fault and the Tonhil Fault forms a wedge of uplifted material in the southwest corner of the basin. Further uplifts surround the basin due to termination thrust splays from the various strike-slip faults. Thus, the structure Shargyn Basin region is a prime example of the features that are common in intraplate transpressional orogenies and the part that pre-existing structural weaknesses can play in defining their locations.

>>>>

	We describe the basin as a combination of two active structures. A left-lateral compressional stepover on the Bogd Fault forms the Khantaishir range and the Shargyn Fault. A conjugate strike-slip intersection between the Bogd Fault and the Tonhil Fault forms a wedge of uplifted material in the southwest corner of the basin. Further uplifts surround the basin due to termination thrust splays from the various strike-slip faults. In addition, the locations of these faults closely follow the local foliation, bedding, or prior faulting planes.  Thus, the structure Shargyn Basin region is a prime example of the features that occur in intraplate transpressional orogenies and the part that pre-existing structural weaknesses can play in defining their locations.

### 2013-05-10 writing/paper/discussion.tex
done with presentation

\subsection{Interpretation and Discussion}
	The Shargyn Basin is a combination of a conjugate strike slip fault intersection and a left-lateral compressional strike-slip stepover. The Bogd Fault to the south, the Tonhil Fault to the west, the Shargyn Fault to the north and the Khantaishir Thrusts to the east are the primary faults governing the structure of the Shargyn Basin. The Bogd Fault and the Shargyn Fault are linked in a compressional stepover by the Khantaishir Thrusts. However, some motion remains on the continuation of the Bogd Fault. The remainder of this motion is transferred into multiple thrust splays, the last of which combines with terminal thrust splays from the Tonhil Fault to form an uplifted region that I will call the intersection wedge. Similar thrust splays on the Shargyn Fault uplift the Dariv Range and link with thrust faults in the Dariv Basin and the Sutai Range. Figure \ref{schematic} shows a schematic diagram of this structure.

@@

	With a kinematic description of the Shargyn Basin in hand, it is interesting to ask why such structures formed in their current locations. One answer to this questions involves pre-existing weaknesses in the crust. Near the stepover, the Bogd Fault bends southward 20-30 degrees. For most of its length, it closely follows the Main Mongolian Lineament. The Main Mongolian Lineament is probably a suture zone and separates a Late Proterozoic and Early Paleozoic orogeny on the north side from a Late Paleozoic orogeny on the south side. The bend in the Bogd Fault may be due to a bend in the Main Mongolian Lineament. \citet{Windley2007} has mapped the Main Mongolian Lineament as bending southwards in this area as well. On a broader scale, the Gobi-Altai and Altai ranges both follow the approximate structural grain in Figure \ref{grain}.

>>>>

\section{Interpretation and Discussion}
	The Shargyn Basin is a combination of a conjugate strike slip fault intersection and a left-lateral compressional strike-slip stepover. The Bogd Fault to the south, the Tonhil Fault to the west, the Shargyn Fault to the north and the Khantaishir Thrusts to the east are the primary faults governing the structure of the Shargyn Basin. The Bogd Fault and the Shargyn Fault are linked in a compressional stepover by the Khantaishir Thrusts. However, some motion remains on the continuation of the Bogd Fault. The remainder of this motion is transferred into multiple thrust splays, the last of which combines with terminal thrust splays from the Tonhil Fault to form an uplifted region that I will call the intersection wedge. Similar thrust splays on the Shargyn Fault uplift the Dariv Range and link with thrust faults in the Dariv Basin and the Sutai Range. Figure \ref{schematic} shows a schematic diagram of this structure.

@@

	With a kinematic description of the Shargyn Basin in hand, it is interesting to ask why such structures formed in their current locations. One answer to this questions involves pre-existing weaknesses in the crust. For most of its length, the Bogd Fault closely follows the Main Mongolian Lineament. he Main Mongolian Lineament is probably a suture zone and separates a Late Proterozoic and Early Paleozoic orogeny on the north side from a Late Paleozoic orogeny on the south side. Near the stepover on the east side of the basin, the Bogd Fault bends southwards 20-30 degrees. This bend in the Bogd Fault may be due to a bend in the Main Mongolian Lineament. \citet{Windley2007} has mapped the Main Mongolian Lineament as bending southwards in this area as well. The trace of the Main Mongolian Lineament through the intersection wedge is shown in \ref{intersection_wedge_joint}. On a broader scale, the Gobi-Altai and Altai ranges both follow the approximate structural grain in Figure \ref{grain}.

### 2013-05-10 writing/paper/main.tex
sending it to oli
removed sections on gravity
finalizing
done with presentation

\documentclass[12pt, doublepage, vi]{mitthesis}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[demo]{graphicx}
\usepackage{natbib}
\usepackage[margin=0.75in]{geometry}
\usepackage{setspace}
\renewcommand\thechapter{}
\renewcommand\thesection{\arabic{section}}
\renewcommand\thesubsection{\thesection.\arabic{subsection}}
\begin{document}
\title{Active deformation of the Shargyn Basin, a transpressional strike-slip intersection in western Mongolia.}
\author{Thomas Ben Thompson}
\department{Department of Earth, Atmospheric and Planetary Science}
\degree{Bachelor of Science in Earth, Atmospheric and Planetary Sciences}
\degreemonth{June}
\degreeyear{2013}
\copyrightnoticetext{\copyright~ 2013 Thomas Ben Thompson \newline
Anyone is permitted to reproduce and distribute copies of thesis so long as they give me credit.}
\thesisdate{May 10, 2013}
\supervisor{Oliver Jagoutz}{Assistant Professor}
\chairman{Samuel Bowring}{Chair, Committee on Undergraduate Program}
\maketitle
\include{abstract}

\section*{Acknowledgments}
Primarily, I thank Claire Bucholz (EAPS PhD candidate) for wandering the Mongolian steppes and mountains and teaching me endlessly about geology and EAPS Professor Oliver Jagoutz for supervising and helping me through the whole thesis process. I thank the UROP office and the EAPS department for supporting my field work in Mongolia last summer.

\tableofcontents
\listoffigures
\clearpage
\include{intro}
\include{background}
\include{structure}
\include{geophysical}
\include{basin}
\include{conclusion}
\bibliographystyle{plainnat}
\bibliography{/home/tbent/projects/library.bib}

>>>>

\documentclass[12pt, doublepage, vi]{mitthesis}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage[margin=0.75in]{geometry}
\usepackage{setspace}
\renewcommand\thechapter{}
\renewcommand\thesection{\arabic{section}}
\renewcommand\thesubsection{\thesection.\arabic{subsection}}
\begin{document}
\title{Active deformation of the Shargyn Basin, a transpressional strike-slip intersection in western Mongolia.}
\author{Thomas Ben Thompson}
\department{Department of Earth, Atmospheric and Planetary Science}
\degree{Bachelor of Science in Earth, Atmospheric and Planetary Sciences}
\degreemonth{June}
\degreeyear{2013}
\copyrightnotice{Thomas Ben Thompson}
\thesisdate{May 10, 2013}
\supervisor{Oliver Jagoutz}{Assistant Professor}
\chairman{Richard P. Binzel}{Chair, Committee on Undergraduate Program}
\maketitle
\include{abstract}

\section*{Acknowledgments}
Primarily, I thank Claire Bucholz (EAPS PhD candidate) for wandering the Mongolian steppes and mountains and teaching me endlessly about geology and EAPS Professor Oliver Jagoutz for supervising and helping me through the whole thesis process. I thank the UROP office and the EAPS department for supporting my field work in Mongolia last summer. I also thank Yeson Erdene and Agi.

\tableofcontents
\listoffigures
\clearpage
\include{intro}
\include{background}
\include{structure}
\include{discussion}
\include{conclusion}
\appendix
\include{xsecappendix}
\bibliographystyle{plainnat}
\bibliography{/home/tbent/projects/library.bib}
